Formulating and Validating RDF Constraints Generically

### 2014-12-30 paper/paper 2/paper 2.tex
implementation

\section{Ideas}

\begin{itemize}
	\item the majority of specific constraints expressed by any specific constraint language can be expressed by DL
	\item each DL statement can be expressed by a generic constraint using a generic constraint language
\end{itemize}

purpose:
\begin{itemize}
	\item translations of specific constraints expressed by any specific constraint language
	\item we do not invent a new constraint languages
\end{itemize}

@@

\begin{itemize}
	\item any specific constraint (expressed by specific constraint language) must be mapped to a generic constraint (expressed by GCL)
\end{itemize}

@@

The \textbf{contributions} of this paper are:
\begin{itemize}
	%\item Any specific constraint (expressed by any constraint language) can be transformed into a generic constraint (expressed by the generic constraint language)
	%\item Any specific constraint (expressed by any constraint language A) can be transformed into any specific constraint (expressed by any constraint language B)
	%\item Any specific constraint (expressed by any constraint language) can be validated automatically (if an automatic validation is defined only once for corresponding generic constraint)
	\item We define a terminology for RDF constraints and constraining languages
	\item We developed an ontology describing any RDF constraint which can also be expressed by any constraint language
	\item We present that any RDF constraint can be described by the developed ontology - whether the constraint can be expressed in DL or not 
	\item We show how to transform specific constraints (expressed by any constraint language A) into generic constraints and into specific constraints (expressed by any other constraint language B)
  \item We explain that any specific constraint can be validated automatically (if an automatic validation is defined only once for corresponding generic constraint)
\end{itemize}

@@

We developed a very simple ontology (three classes, three object properties, and three data properties) which is universal enough to describe any RDF constraint expressible by any RDF constraint language.
We distinguish between two sub-types of \ms{constraint}: 
\begin{itemize}
	\item \ms{property constraints} and 
	\item \ms{class constraints}. 
\end{itemize}

@@

\section{Automatic Validation of Specific Constraints}

@@

We provide a mapping from the generic constraint language to SPIN\footnote{GCL SPIN mapping: \url{https://github.com/boschthomas/GCL-SPIN-Mapping}} in order to automatically validate each type of generic constraint (simple, complex, property, and class constraints).
Part of future work will be 
\begin{itemize}
	\item to provide a GUI which generates generic constraints automatically according to inputs of domain experts who are not familiar with the formulation of constraints.
	\item to extend our RDF validator to provide bidirectional transformations between specific constraints (expressed by multiple constraint languages) and generic constraints. 
\end{itemize}

@@

Constraints can be classified as \ms{property constraints} and \ms{class constraints}.
Two thirds are property constraints, one fifth class constraints, and approx. 10\% are composed of both property and class constraints.
Constraints may be either atomic (\ms{simple constraints}) or created out of simple and complex constraints (\ms{complex constraints}).
Almost two thirds are simple constraints, a quarter are complex constraints.
Almost 15 percent are complex constraints which can be formulated as simple constraints when used in terms of syntactic sugar.
Constraints can either be expressible in DL or not.
Nearly 70\% of the overall constraints are expressible in DL.

>>>>

%\section{Ideas}

@@

@@

The \textbf{contributions} of this paper are:
\begin{itemize}
	%\item Any specific constraint (expressed by any constraint language) can be transformed into a generic constraint (expressed by the generic constraint language)
	%\item Any specific constraint (expressed by any constraint language A) can be transformed into any specific constraint (expressed by any constraint language B)
	%\item Any specific constraint (expressed by any constraint language) can be validated automatically (if an automatic validation is defined only once for corresponding generic constraint)
	\item We define a terminology for RDF constraints and constraining languages
	\item We developed an ontology describing any RDF constraint which can also be expressed by any constraint language
	\item We present that any RDF constraint can be described by the developed ontology - whether the constraint can be expressed in DL or not 
	\item We show how to transform specific constraints (expressed by any constraint language A) into generic constraints and into specific constraints (expressed by any other constraint language B)
  \item We explain that any specific constraint can be validated automatically (if an automatic validation is defined only once for the corresponding generic constraint)
\end{itemize}

@@

We developed a very simple ontology (three classes, three object properties, and three data properties) which is universal enough to describe any RDF constraint expressible by any RDF constraint language.
Therefore, we do not invent a new constraint language.
We distinguish between two sub-types of \ms{constraint}: 
\begin{itemize}
	\item \ms{property constraints} and 
	\item \ms{class constraints}. 
\end{itemize}

@@

@@

We provide a mapping from the generic constraint language to SPIN\footnote{GCL SPIN mapping: \url{https://github.com/boschthomas/GCL-SPIN-Mapping}} in order to automatically validate each type of generic constraint (simple, complex, property, and class constraints).
Part of future work will be 
\begin{itemize}
	\item to provide a GUI which generates generic constraints automatically according to inputs of domain experts who are not familiar with the formulation of constraints.
	\item to offer bidirectional transformations between specific constraints (expressed by multiple constraint languages) and generic constraints. 
	\item to provide translations between specific constraints (expressed by any specific constraint language) by using generic constraints as an intermediate transformation step.
\end{itemize}

@@

Constraints can be classified as \ms{property constraints} and \ms{class constraints}.
Two thirds are property constraints, one fifth class constraints, and approx. 10\% are composed of both property and class constraints.
Constraints may be either atomic (\ms{simple constraints}) or created out of simple and complex constraints (\ms{complex constraints}).
Almost two thirds are simple constraints, a quarter are complex constraints.
Almost 15 percent are complex constraints which can be formulated as simple constraints when used in terms of syntactic sugar.
Constraints can either be expressible in DL or not.
The majority - nearly 70\% - of the overall constraints are expressible in DL.
